Modal Abstractions for Virtualizing Memory Addresses

### 2023-03-29 programlogic.tex
+

Based on these perspectives, we coneptualize truth on an address-space as indexed by its roots address, therefore. we lift standard bi proposition to be indexed with $\mathcal{W}_{64}$ as shown in Figure \ref{fig:vprop}. Contesequently. all abstractions we explain in this section as part of our address-space logic are type $\textsf{vProp }\Sigma$.

>>>>

Based on these perspectives, we coneptualize truth on an address-space through the contingency it exhibits: \textit{assertion P holds on this address-space indexed by its roots address}, Therefore. we lift standard bi proposition to be indexed with $\mathcal{W}_{64}$ as shown in Figure \ref{fig:vprop}. In other words, all abstractions we explain in this section as part of our address-space logic are type $\textsf{vProp }\Sigma$.
